R Notebook

### 2017-03-31 doc/RMD/MLG-distribution.Rmd
whoops. place circle in front of edge

glay <- create_layout(gnew, "manual", node.positions = as.data.frame(glayout2) %>% setNames(c("x", "y")))
ggraph(glay) +
  geom_node_circle(aes(r = scale(size, center = FALSE)/10, fill = size, alpha = 1 - weight)) +
  geom_edge_fan() +
  # geom_edge_fan2(aes(start_cap = circle(rep(spac$from_size, 2)/2, "mm"),
  #                   end_cap = circle(rep(spac$to_size, 2)/2, "mm"))) +
  geom_node_label(aes(label = name), repel = TRUE) +
  viridis::scale_fill_viridis(option = "C") +
  coord_fixed() +
  theme_void() +
  labs(list(
    title = "Shared haplotypes across regions",
    fill = "Number of\nGenotypes",
    alpha = "Fraction of private genotpes",
    caption = "Outer circle: Number of genotypes in the region\nInner Circle: Number of private genotypes in the region"
  ))
```

>>>>

glay <- create_layout(gnew, "manual", node.positions = as.data.frame(glayout2) %>% setNames(c("x", "y")))
ggraph(glay) +
  geom_edge_fan() +
  # geom_edge_fan2(aes(start_cap = circle(rep(spac$from_size, 2)/2, "mm"),
  #                   end_cap = circle(rep(spac$to_size, 2)/2, "mm"))) +
  geom_node_circle(aes(r = scale(size, center = FALSE)/10, fill = size, alpha = 1 - weight)) +
  geom_node_label(aes(label = name), repel = TRUE) +
  viridis::scale_fill_viridis(option = "C") +
  coord_fixed() +
  theme_void() +
  labs(list(
    title = "Shared haplotypes across regions",
    fill = "Number of\nGenotypes",
    alpha = "Fraction of private genotpes",
    caption = "Outer circle: Number of genotypes in the region\nInner Circle: Number of private genotypes in the region"
  ))
```
